preregistration

### 2022-03-23 preregistrations/2_study1/preregistration.Rmd
Amendment to Preregistration of Study 1

After providing consent, participants started with the Flanker Task. They were asked to complete the Flanker Task in a quiet room in the house where they would be least likely to be distracted by other people or outside noises. The order of the tasks was counterbalanced between subjects. At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs. The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015]. Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen until it matched the size of the creditcard. The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants. After successfully resizing the screen, participants completed all three tasks. During the task, the cursor was hidden from the screen to minimize distractions. Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).

@@

>>>>

After providing consent, participants started with the Flanker Task. They were asked to complete the Flanker Task in a quiet room in the house where they would be least likely to be distracted by other people or outside noises. The order of the tasks was counterbalanced between subjects. At the onset of the first task, the experiment went into full-screen mode to limit distractions from other programs or browser tabs. The size of the task stimuli was controlled between subjects using the resize plugin in JsPsych [@deLeeuw_2015]. Participants were asked to hold a creditcard (or similarly sized card) up against the screen and to increase the size of a blue rectangle on the screen (initial size 300 pixels) until it matched the size of the creditcard. The stimulus display for each task was resized so that 100 pixels corresponded to 1 inch for all participants. After successfully resizing the screen, participants completed all three tasks. During the task, the cursor was hidden from the screen to minimize distractions. Code for the three tasks can be found on [Github](https://github.com/StefanVermeent/attention_project/tree/main/tasks).

@@

**Amendment to preregistration prior to data analysis:** In the current study, we made a change to the screen rescaling procedure using a credit card. Specifically, we changed to initial size of the resize box from 100px to 300px. This way, the stimulus display would still be reasonably close to the intended size if participants did not engage in any resizing. However, this led to a change between the pilot study and the current study, which is particularly important for the pooled analysis as rescaling (yes or no) was included as an arbitrary exclusion decision in the multiverse analyses. To solve this issue, we decided to include this decision with four combinations: 1) exclude non-scalers in both studies; 2) include non-scalers in both studies; 3) exclude non-scalers in pilot study, include non-scalers in study 1; 4) include non-scalers in pilot study, exclude non-scalers in study 1.
